---
title: "simpleRegress"
author: "Brennen Long"
date: "4/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set up regression models

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

# NECK
## Model LENGTH ~ NECK    

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=bears$NECK [c(5, 15, 23)])
predict(simp,new,se.fit=TRUE)
```

# HEADWTH
## Model LENGTH ~ HEADWTH 

```{r}
simpHW <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simpHW)
summary.lm(simpHW)
```

```{r}
new <- data.frame(HEADWTH=bears$HEADWTH [c(5, 15, 23)])
predict(simpHW,new,se.fit=TRUE)
```


# HEADLEN
## Model LENGTH ~ HEADLEN

```{r}
simpHL <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simpHL)
summary.lm(simpHL)
```

```{r}
new <- data.frame(HEADLEN=bears$HEADLEN [c(5, 15, 23)])
predict(simpHL,new,se.fit=TRUE)
```


# WEIGHT
## Model LENGTH ~ WEIGHT

```{r}
simpWT <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simpWT)
summary.lm(simpWT)
```

```{r}
new <- data.frame(WEIGHT=bears$WEIGHT [c(5, 15, 23)])
predict(simpWT,new,se.fit=TRUE)
```


# CHEST
## Model LENGTH ~ CHEST

```{r}
simpCT <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simpCT)
summary.lm(simpCT)
```


## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

